Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-05-10 writeup.Rmd
fixed the equations, ready for final review

To analyze the effect of link and response options on inferred implicature rate, we used a Bayesian binomial mixed effects model using the R packge "brms" [@burkner2016brms] with uninformative or weakly informative priors [^3]. The model predicted the log odds of implicature over no implicature from fixed effects of *response type* (binary, ternary, quaternary, quinary -- dummy-coded with binary as reference level), *link* (strong vs. weak -- dummy-coded with strong as reference level), and trial type (exhaustive vs. scalar -- dummy-coded, with exhaustive as reference level), as well as their two-way and three-way interactions. Following @barr2013random, we included the maximal random effects structure justified by the design: random intercepts for items (cards) and participants, random by-participant slopes for link, trial type, and their interaction, and random by-item slopes for link, trial type, response type, and their interactions. Since the number of response options was a between participant variable we did not include random slopes of response options for participants. Four chains converged after 2000 iterations each (warmup = 1000). Table \@ref(tab:modeltable) summarizes the mean parameter estimates and their 95% credible intervals. $\hat{R}=1$ for all estimated parameters. All the analytical decisions described here were pre-registered[^3].

[^3: For more information about the default priors of the "brms" package, see [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).]

@@

[^3]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)

@@

$$

    P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s) \\

    P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) \\

    P_{L_0}(s | u) \propto [[u]](s) * P_w(s)

$$

>>>>

To analyze the effect of link and response options on inferred implicature rate, we used a Bayesian binomial mixed effects model using the R packge "brms" [@burkner2016brms] with uninformative or weakly informative priors [^3]. The model predicted the log odds of implicature over no implicature from fixed effects of *response type* (binary, ternary, quaternary, quinary -- dummy-coded with binary as reference level), *link* (strong vs. weak -- dummy-coded with strong as reference level), and trial type (exhaustive vs. scalar -- dummy-coded, with exhaustive as reference level), as well as their two-way and three-way interactions. Following @barr2013random, we included the maximal random effects structure justified by the design: random intercepts for items (cards) and participants, random by-participant slopes for link, trial type, and their interaction, and random by-item slopes for link, trial type, response type, and their interactions. Since the number of response options was a between participant variable we did not include random slopes of response options for participants. Four chains converged after 2000 iterations each (warmup = 1000). Table \@ref(tab:modeltable) summarizes the mean parameter estimates and their 95% credible intervals. $\hat{R}=1$ for all estimated parameters. All the analytical decisions described here were pre-registered[^5].

[^3]: For more information about the default priors of the "brms" package, see [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).

@@

[^5]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)

@@

$P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$

$P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u)))$

$P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$

### 2018-05-10 writeup.tex
some version
fixed the equations, ready for final review

To analyze the effect of link and response options on inferred
implicature rate, we used a Bayesian binomial mixed effects model using
the R packge \enquote{brms} (Bürkner \& others, 2016) with uninformative
or weakly informative priors.\footnote{You can access our
  pre-registration at \url{https://aspredicted.org/tq3sz.pdf}} The model
predicted the log odds of implicature over no implicature from fixed
effects of \emph{response type} (binary, ternary, quaternary, quinary --
dummy-coded with binary as reference level), \emph{link} (strong
vs.~weak -- dummy-coded with strong as reference level), and trial type
(exhaustive vs.~scalar -- dummy-coded, with exhaustive as reference
level), as well as their two-way and three-way interactions. Following
Barr, Levy, Scheepers, and Tily (2013), we included the maximal random
effects structure justified by the design: random intercepts for items
(cards) and participants, random by-participant slopes for link, trial
type, and their interaction, and random by-item slopes for link, trial
type, response type, and their interactions. Since the number of
response options was a between participant variable we did not include
random slopes of response options for participants. Four chains
converged after 2000 iterations each (warmup = 1000). Table
\ref{tab:modeltable} summarizes the mean parameter estimates and their
95\% credible intervals. \(\hat{R}=1\) for all estimated parameters. All
the analytical decisions described here were pre-registered\footnote{You
  can access our pre-registration at
  \url{https://aspredicted.org/tq3sz.pdf}}.

{[}\^{}3: For more information about the default priors of the
\enquote{brms} package, see
\href{ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf}{the
brms package manual}.{]}

@@

\$\$

\begin{verbatim}
P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s) \\

P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) \\

P_{L_0}(s | u) \propto [[u]](s) * P_w(s)
\end{verbatim}

\$\$

>>>>

To analyze the effect of link and response options on inferred
implicature rate, we used a Bayesian binomial mixed effects model using
the R packge \enquote{brms} (Bürkner \& others, 2016) with uninformative
or weakly informative priors.\footnote{For more information about the
  default priors of the \enquote{brms} package, see
  \href{ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf}{the
  brms package manual}.} The model predicted the log odds of implicature
over no implicature from fixed effects of \emph{response type} (binary,
ternary, quaternary, quinary -- dummy-coded with binary as reference
level), \emph{link} (strong vs.~weak -- dummy-coded with strong as
reference level), and trial type (exhaustive vs.~scalar -- dummy-coded,
with exhaustive as reference level), as well as their two-way and
three-way interactions. Following Barr, Levy, Scheepers, and Tily
(2013), we included the maximal random effects structure justified by
the design: random intercepts for items (cards) and participants, random
by-participant slopes for link, trial type, and their interaction, and
random by-item slopes for link, trial type, response type, and their
interactions. Since the number of response options was a between
participant variable we did not include random slopes of response
options for participants. Four chains converged after 2000 iterations
each (warmup = 1000). Table \ref{tab:modeltable} summarizes the mean
parameter estimates and their 95\% credible intervals. \(\hat{R}=1\) for
all estimated parameters. All the analytical decisions described here
were pre-registered\footnote{You can access our pre-registration at
  \url{https://aspredicted.org/tq3sz.pdf}}.

@@

\(P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)\)

\(P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u)))\)

\(P_{L_0}(s | u) \propto [[u]](s) * P_w(s)\)
